### 2022-06-27 input/appendices.tex
quick format
lowering page number, still long way to go 23 over 20

\appendices

@@

\begin{table*}
  \centering
  \caption{\label{table:notations}Notation table.}
  \begin{tabularx}{\textwidth}{@{}lll@{}}
    \toprule
    Notation & Short & Description \\
    \midrule

    $G$ & \underline{G}raph    & Represents a network.\\
    $V$ & \underline{V}ertices & Represents the set of nodes, or processes.\\
    $E$ & \underline{E}dges    & Represents the set of asynchronous communication links.\\
    $w_{xy}$     & \underline{w}eight & Positive weight of the edge $\langle x, y \rangle$.\\
    $\pi_{xz}$ and $\Pi_{xz}$  & \underline{p}ath and best \underline{P}ath & List of contiguous edges from \Process $x$ to \Process $z$.\\
    $|\pi_{xz}|$ and $|\Pi_{xz}|$ & sum of path weights & Positive sum of weights of the path.\\

    \midrule

    $\sigma_x$  & \underline{s}tate     & The local state of \Process $x$.\\
    $b_x(m)$    & \underline{b}roadcast & \Process $x$ creates a new message $m$ that must be delivered by all \processes.\\
    $d_{x}(m)$  & \underline{d}eliver   & \Process $x$ delivers the message $m$.\\
    $r_y(m)$ or $r_{yx}(m)$  & \underline{r}eceive   & \Process $y$ receives the message $m$ from any neighboring node or \Process $x$ if specified.\\
    $s_{xy}(m)$ & \underline{s}end      & \Process $x$ sends the message $m$ to \Process $y$.\\
    $f_x(m)$    & \underline{f}orward   & \Process $x$ forwards the message $m$ to its neighbors.\\
    $m \oplus \sigma$   & aggregator    & Aggregates $\sigma$ into the metadata of message $m$.\\
    $\phi(\mu, \sigma)$ & predicate \underline{f}unction & Checks the metadata $\mu$ using the state $\sigma$.\\
    $\eventually P$     & eventually    & Eventually predicate $P$ is true.\\
    $e_1 \rightarrow e_2$ & happens before  & The event $e_1$ happened before the event $e_2$. Delivery, sending, or receipt are events.\\
    $D_x$ & \underline{D}elivered & Set of delivered messages by \Process $x$.\\

    \midrule

    $\alpha_x^d$ or $\alpha_{\pi_{xz}}^d$      & \underline{a}dd source & Message that notifies the adding of Source $x$ in the network.\\
    $\delta_x$   & source \underline{d}eletion & Message that notifies the deletion of Source $x$, or the detection by \Process $x$ of a possible source deletion.\\
    $\mathcal{S}(m)$ & \underline{S}tale message & Message $m$ conveys stale control information since its broadcaster broadcast a newer message.\\

    \bottomrule
  \end{tabularx}
\end{table*}

>>>>

\appendix

@@

\input{input/tablenotations.tex}

### 2022-06-27 input/experiments.tex
lowering page number, still long way to go 23 over 20

\newcommand{\FIGSCALE}{0.99}

@@

\begin{figure}
  \centering\includegraphics[width=\FIGSCALE\columnwidth]{img/as_cast_complexity.pdf}
  \caption{\label{fig:complexity}Dynamic consistent partitioning overhead of \NAME.}

  %% \caption{\label{fig:complexity}Cumulative average number of messages
  %%   per process in a network comprising 10k processes; along with the
  %%   duration before reaching consistent partitioning after adding or
  %%   removing a partition, totaling 100 new partition then removed.}
\end{figure}

@@

\begin{figure}
  \centering\includegraphics[width=\FIGSCALE\columnwidth]{img/as_cast_geant.pdf}
  \caption{\label{fig:geant}Overhead of \NAME in the partitioning of 2
    clusters connected by a long distance link.}
\end{figure}

@@

\begin{figure*}
  \subfloat[\label{fig:nrens}Workload in 40 interconnected autonomous systems with
    1157 \processes~\cite{knight2011internet}.]{
    \includegraphics[width=\FIGSCALE\columnwidth]{img/europe-ases.pdf} 
  }
  \hspace{5pt}
  \subfloat[\label{fig:europe-ases}Traffic overhead and maintained indexes.]{
    \centering\includegraphics[width=\FIGSCALE\columnwidth]{img/europe_as_vs_xas.pdf}
  }
  \caption{Limitations of \NAME and evaluation of \NAMEC for lazy dynamic partitioning.}
\end{figure*}

>>>>

\newcommand{\FIGSCALE}{0.48}

@@

\begin{figure*}[t]
  \subfloat[\label{fig:complexity}Dynamic consistent partitioning overhead of \NAME.]{
    \includegraphics[width=\FIGSCALE\columnwidth]{img/as_cast_complexity.pdf} 
  }
  \hspace{5pt}
  \subfloat[\label{fig:geant}Partitioning overhead of 2
    clusters connected by a long distance link.]{
    \centering\includegraphics[width=\FIGSCALE\columnwidth]{img/as_cast_geant.pdf}
  }
  \caption{\TODO{\NAME overhead}.}
\end{figure*}

%% \begin{figure}[t]
%%   \centering\includegraphics[width=\FIGSCALE\columnwidth]{img/as_cast_complexity.pdf}
%%   \caption{\label{fig:complexity}Dynamic consistent partitioning overhead of \NAME.}

%%   %% \caption{\label{fig:complexity}Cumulative average number of messages
%%   %%   per process in a network comprising 10k processes; along with the
%%   %%   duration before reaching consistent partitioning after adding or
%%   %%   removing a partition, totaling 100 new partition then removed.}
%% \end{figure}

@@

%% \begin{figure}[t]
%%   \centering\includegraphics[width=\FIGSCALE\columnwidth]{img/as_cast_geant.pdf}
%%   \caption{\label{fig:geant}Partitioning overhead of 2
%%     clusters connected by a long distance link.}
%% \end{figure}

@@

\begin{figure*}[t]
  \subfloat[\label{fig:nrens}Workload in 40 interconnected autonomous systems with
    1157 \processes~\cite{knight2011internet}.]{
    \includegraphics[width=\FIGSCALE\columnwidth]{img/europe-ases.pdf} 
  }
  \hspace{5pt}
  \subfloat[\label{fig:europe-ases}Traffic overhead and maintained indexes.]{
    \centering\includegraphics[width=\FIGSCALE\columnwidth]{img/europe_as_vs_xas.pdf}
  }
  \caption{Evaluation of \NAMEC for \emph{lazy} dynamic partitioning.}
\end{figure*}

### 2022-06-27 input/figundoproblem.tex
meow
lowering page number, still long way to go 23 over 20

\begin{figure*}
  \newcommand{\SCALE}{0.9}

@@

  \newcommand\X{50pt}
  \newcommand\Y{-50pt}

@@

  \begin{center}
    \subfloat[Part A][\label{fig:undoproblemA}$a$ and $c$ become sources.
      $w_{ab} = 2$; $w_{bc} = 1$.]{\input{input/figundoproblemA.tex}}
    \hspace{5pt}
    \subfloat[Part B][\label{fig:undoproblemB}$c$ deletes its partition but $a$ does not.
      $b$ delivers and forwards $\alpha_a$.]
             {\input{input/figundoproblemB.tex}}
    \hspace{5pt}
    \subfloat[Part C][\label{fig:undoproblemC}$b$ delivers and forwards $\alpha_c$.]
             {\input{input/figundoproblemC.tex}}
    \hspace{5pt}
    \subfloat[Part D][\label{fig:undoproblemD}$b$ delivers and forwards $\delta_c$.]
             {\input{input/figundoproblemD.tex}}
    \hspace{5pt}
    \subfloat[Part E][\label{fig:undoproblemE}$a$ echoes back $\alpha_a^2$ that $b$ needs.]
             {\input{input/figundoproblemE.tex}}
    \hspace{5pt}
    \subfloat[Part F][\label{fig:undoproblemF}$a$, $b$, and $c$ belong to $P_a$.]
             {\input{input/figundoproblemF.tex}}
  \end{center}
  \caption{\label{fig:undoproblem}From $c$'s perspective,
    Figure~\ref{fig:problemE} and Figure~\ref{fig:undoproblemE} are
    similar in terms of received messages, but the outcomes eventually
    differ. Yet, $c$ must act on Figure~\ref{fig:undoproblemE}, and
    acknowledge then propagate the \emph{possible} staleness of its
    partition $P_a$.}
\end{figure*}

>>>>

\begin{figure*}[t]
  \newcommand{\SCALE}{0.8}

@@

  \newcommand\X{42pt}
  \newcommand\Y{-40pt}

@@

  \begin{center}
    \subfloat[Part A][\label{fig:undoproblemA}$a$ and $c$ become sources.
      $w_{ab} = 2$; $w_{bc} = 1$.]{\input{input/figundoproblemA.tex}}
    \hspace{5pt}
    \subfloat[Part B][\label{fig:undoproblemB}$c$ deletes its partition but $a$ does not.
      $b$ delivers and forwards $\alpha_a$.]
             {\input{input/figundoproblemB.tex}}
    \hspace{5pt}
    \subfloat[Part C][\label{fig:undoproblemC}$b$ delivers + forwards $\alpha_c$.]
             {\input{input/figundoproblemC.tex}}
    \hspace{5pt}
    \subfloat[Part D][\label{fig:undoproblemD}$b$ delivers + forwards $\delta_c$.]
             {\input{input/figundoproblemD.tex}}
    \hspace{5pt}
    \subfloat[Part E][\label{fig:undoproblemE}$a$ echoes back $\alpha_a^2$ to $b$.]
             {\input{input/figundoproblemE.tex}}
    \hspace{5pt}
    \subfloat[Part F][\label{fig:undoproblemF}$a$, $b$, $c$ belong to $P_a$.]
             {\input{input/figundoproblemF.tex}}
  \end{center}
  \caption{\label{fig:undoproblem}From $c$'s perspective,
    Figure~\ref{fig:problemE} and Figure~\ref{fig:undoproblemE} are
    similar in terms of received messages, but the outcomes eventually
    differ. Yet, $c$ must act on Figure~\ref{fig:undoproblemE}, and
    acknowledge then propagate the \emph{possible} staleness of
    Partition $P_a$.}
\end{figure*}

### 2022-06-27 input/proposal.tex
quick format
lowering page number, still long way to go 23 over 20

This definition encompasses more specific definitions of related
work~\cite{hsiao2005scoped, lue2006scoped, wang2015prodiluvian}. It
underlines the transitive relevance of messages. It also highlights
that the functioning of epidemic propagation is well-aligned with the
objectives of scoped broadcast. As consequence, we assume
implementations relying on the forwarding of messages from
neighbor-to-neighbor.

@@

\begin{algorithm}
  \input{input/algoadd.tex}
  \caption{\label{algo:add}Add-only CP protocol at \Process~$p$.}
\end{algorithm}

@@

  \vspace{-1.5em} %% ugly vspace but necessary for enumerate+qed

@@

\begin{algorithm}
  \input{input/algoascast.tex}
  \caption{\label{algo:ascast}\NAME: DCP protocol at \Process~$p$.}
\end{algorithm}

@@

\begin{algorithm}[h]
  \input{input/algoedges.tex}
  \caption{\label{algo:edges}\NAME at \Process~$p$ in dynamic networks.}
\end{algorithm}

>>>>

This definition encompasses more specific definitions of related
work~\cite{hsiao2005scoped,lue2006scoped,wang2015prodiluvian}. It
underlines the transitive relevance of messages. It also highlights
that the functioning of epidemic propagation is well-aligned with the
objectives of scoped broadcast. As consequence, we assume
implementations relying on the forwarding of messages from
neighbor-to-neighbor.

@@

\begin{algorithm}[t]
  \input{input/algoadd.tex}
  \caption{\label{algo:add}Add-only CP protocol at \Process~$p$.}
\end{algorithm}

@@

  % \vspace{-1.5em} %% ugly vspace but necessary for enumerate+qed

@@

\begin{algorithm}[t]
  \input{input/algoascast.tex}
  \caption{\label{algo:ascast}\NAME: DCP protocol at \Process~$p$.}
\end{algorithm}

@@

\begin{algorithm}[t]
  \input{input/algoedges.tex}
  \caption{\label{algo:edges}\NAME at \Process~$p$ in dynamic networks.}
\end{algorithm}

### 2022-06-27 input/related_work.tex
lowering page number, still long way to go 23 over 20

\noindent The most closely related approaches to \NAME come from
\underline{i}nformation-\underline{c}entric \underline{n}etworking
(ICN)~\cite{garcia-lopez, hemmati2015namebased} and distributed
clustering~\cite{sohier2012physarum}. The sources advertise themselves
periodically. Advertisements either stop as soon as they reach
uninterested \processes~\cite{garcia-lopez, hemmati2015namebased}, or
propagate through most likely interested
\processes~\cite{sohier2012physarum}. However their cyclic operation
requires that
\begin{inparaenum}[(i)]
\item they constantly generate traffic even in quiescent systems where
  \processes do not add nor destroy replicas; and 
\item they either operate in synchronous
  systems~\cite{barjon2014maintaining, sohier2012physarum} or must define
  physical-clock-based timeouts the value of which depends on network
  topology properties such as network diameter~\cite{garcia-lopez,
    hemmati2015namebased}.
  %also incur an overhead even in quiet contexts without any update.
  % Moreover, they necessarily rely on physical timeouts
  Unfitting timeouts lead to premature removals of live replicas; or
  slow convergence where \processes wrongly believe that their closest
  replica is live while it was destroyed.
\end{inparaenum}
On the opposite, \NAME quickly informs each \process of its closest
replica even in large and dynamic networks with asynchronous
communications; and has no overhead in quiescent systems.

>>>>

\noindent The most closely related approaches to \NAME come from
\underline{i}nformation-\underline{c}entric \underline{n}etworking
(ICN)~\cite{garcia-lopez,hemmati2015namebased} and distributed
clustering~\cite{sohier2012physarum}. The sources advertise themselves
periodically. Advertisements either stop as soon as they reach
uninterested \processes~\cite{garcia-lopez,hemmati2015namebased}, or
propagate through most likely interested
\processes~\cite{sohier2012physarum}. However their cyclic operation
requires that
\begin{inparaenum}[(i)]
\item they constantly generate traffic even in quiescent systems where
  \processes do not add nor destroy replicas; and 
\item they either operate in synchronous
  systems~\cite{barjon2014maintaining,sohier2012physarum} or must define
  physical-clock-based timeouts the value of which depends on network
  topology properties such as network diameter~\cite{garcia-lopez,hemmati2015namebased}.
  %also incur an overhead even in quiet contexts without any update.
  % Moreover, they necessarily rely on physical timeouts
  Unfitting timeouts lead to premature removals of live replicas; or
  slow convergence where \processes wrongly believe that their closest
  replica is live while it was destroyed.
\end{inparaenum}
On the opposite, \NAME quickly informs each \process of its closest
replica even in large and dynamic networks with asynchronous
communications; and has no overhead in quiescent systems.
